Accurate inference of microbial differential abundance from taxonomically-biased microbiome measurements

### 2021-09-09 abundance-measurement.Rmd
Change method of rendering SVGs in PDF output
Previously, I used the cowplot R package to display the SVG images in
the PDF rendering; however, this requires the 'magick' Latex package and
does not always seem to give good results. I now use Inkscape to convert
the SVG to a PDF file in a temporary directory and import this figure
with knitr.

```{r error-proportions, out.width = '90%', fig.cap = '(ref:cap-error-proportions)', cache = TRUE}
svg_path <- here("figures/illustrations/error-proportions.svg")
if (knitr::is_html_output()) {
  knitr::include_graphics(svg_path)
} else if (knitr::is_latex_output()) {
  cowplot::ggdraw() + cowplot::draw_image(svg_path)
}
rm(svg_path)
```

>>>>

```{r error-proportions, out.width = '90%', fig.cap = '(ref:cap-error-proportions)', cache = TRUE}
svg_path <- here("figures/illustrations/error-proportions.svg")
if (knitr::is_html_output()) {
  knitr::include_graphics(svg_path)
} else if (knitr::is_latex_output()) {
  # cowplot::ggdraw() + cowplot::draw_image(svg_path)
  pdf_path <- file.path("/tmp", "bookdown-differential-abundance-theory",
    "error-proportions.pdf")
  args <- c(
    "--export-area-page", 
    "--export-type=pdf", 
    str_c("--export-filename=", pdf_path),
    svg_path
  )
  system2("inkscape", args = args)
  knitr::include_graphics(pdf_path)
}
rm(svg_path, pdf_path)
```

### 2021-09-09 differential-abundance.Rmd
Change method of rendering SVGs in PDF output
Previously, I used the cowplot R package to display the SVG images in
the PDF rendering; however, this requires the 'magick' Latex package and
does not always seem to give good results. I now use Inkscape to convert
the SVG to a PDF file in a temporary directory and import this figure
with knitr.

```{r regression-example, fig.cap = '(ref:regression-example)'}
svg_path <- here::here(
  "notebook/_posts/2021-08-03-simulate-regression-example/",
  "simulate-regression-example_files/figure-html5/",
  "main-figure-1.svg"
)
if (knitr::is_html_output()) {
  knitr::include_graphics(svg_path)
} else if (knitr::is_latex_output()) {
  cowplot::ggdraw() + cowplot::draw_image(svg_path)
}
rm(svg_path)
```

>>>>

```{r regression-example, fig.cap = '(ref:regression-example)'}
svg_path <- here::here(
  "notebook/_posts/2021-08-03-simulate-regression-example/",
  "simulate-regression-example_files/figure-html5",
  "main-figure-1.svg"
)
if (knitr::is_html_output()) {
  knitr::include_graphics(svg_path)
} else if (knitr::is_latex_output()) {
  # cowplot::ggdraw() + cowplot::draw_image(svg_path)
  pdf_path <- file.path("/tmp", "bookdown-differential-abundance-theory",
    "regression-example.pdf")
  args <- c(
    "--export-area-page", 
    "--export-type=pdf", 
    str_c("--export-filename=", pdf_path),
    svg_path
  )
  system2("inkscape", args = args)
  knitr::include_graphics(pdf_path)
}
rm(svg_path, pdf_path)
```
